SpARC: Sparse Redundant Calibration

### 2016-09-26 paper.tex
added some references
started adding geometry mapping

We will be using the following SNR (signal-to-noise ratio) definition in this paper  
\begin{equation}
\textrm{SNR} = \frac{<\bv\odot\conj{\bv}>_{t,pq}}{<\bn\odot\conj{\bn}>_{t,pq}}, 
\end{equation}
where $<*>_{t,pq}$ denotes averaging over time and baselines and $\odot$ denotes the Hadamard product. The definition we use here is similar 
to the SNR definitions that were used in ??,??.

and $n_{pq}$ 
zero-mean gaussian noise representing thermal noise.

>>>>

We will be using the following SNR (signal-to-noise ratio) definition in this paper  
\begin{equation}
\textrm{SNR} = \frac{<\bv\odot\conj{\bv}>_{t,pq}}{<\bn\odot\conj{\bn}>_{t,pq}}, 
\end{equation}
where $<*>_{t,pq}$ denotes averaging over time and baselines and $\odot$ denotes the Hadamard product. The definition we use here is similar 
to the SNR definitions of \citet{Liu2010,Marthi2014}.

\subsection{Redundant Array Geometry Mapping}
If an array is redundant then its redundant baselines sample the exact same visibilites in the $uv$-plane, i.e. if baseline $pq$ and $rs$ are redundant then $y_{pq} = y_{rs}$. We can
therefore also use the following useful indexing strategy: we can use singular redundant baseline indexes instead of composite antenna pairs to label the true observed visibilities.
